### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@6b0bf45bcca3c5087278c6e20f4b0df04edcef44 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@3cbf9a2f9d29a07718d0e876dab9484dcc411514 🚀

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple) and right
(green/brown) subspaces, alongside the adjacency matrix of the food web
they encode (greyscale). The European metaweb is on the left, and the
imputed Canadian metaweb (before data inflation) on the right. This
figure illustrates how much structure the left subspace captures. As we
show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
subspace are species without any prey.}\label{fig:subspaces}
}
\end{figure}

@@

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institute
for Ecology \& Evolution. FB is funded by the Institute for Data
Valorization (IVADO). TS, SB, and TP are funded by a donation from the
Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
IT12391, in partnership with fRI Research, and also acknowledges funding
from Alberta Innovates and the Forest Resources Improvement Association
of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
Tuku Iho National Science Challenge, administered by New Zealand
Ministry of Business, Innovation, and Employment. BM is funded by the
NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT
master's scholarship. LP acknowledges funding from NSERC Discovery Grant
(NSERC RGPIN-2019-05771). TP acknowledges financial support from NSERC
through the Discovery Grants and Discovery Accelerator Supplement
programs.

>>>>

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple; left side
matrix) and right (green/brown; top matrix) subspaces, alongside the
adjacency matrix of the food web they encode (greyscale). The European
metaweb is on the left, and the imputed Canadian metaweb (before data
inflation) on the right. This figure illustrates how much structure the
left subspace captures. As we show in fig.~\ref{fig:degree}, the species
with a value of 0 in the left subspace are species without any
prey.}\label{fig:subspaces}
}
\end{figure}

@@

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institute
for Ecology \& Evolution. FB is funded by the Institute for Data
Valorization (IVADO). TS, SB, and TP are funded by a donation from the
Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
IT12391, in partnership with fRI Research, and also acknowledges funding
from Alberta Innovates and the Forest Resources Improvement Association
of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
Tuku Iho National Science Challenge, administered by New Zealand
Ministry of Business, Innovation, and Employment. BM is funded by the
NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT
master's scholarship. LP acknowledges funding from NSERC Discovery Grant
(NSERC RGPIN-2019-05771). TP acknowledges financial support from NSERC
through the Discovery Grants and Discovery Accelerator Supplement
programs. MJF is supported by an NSERC PDF and an RBC Post-Doctoral
Fellowship
